---
name: Damian Fiłonowicz
position: "Data Engineering student, date of birth: 08.02.1998"
address: "Poland, Gdańsk University of Technology"
phone: 662 515 228
email: damianomancity@gmail.com
linkedin: kangshung
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: 'I am a 21-year-old aspiring Data Engineering student who seeks a job as a Data Scientist/Data Engineer.'
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
pacman::p_load(vitae, tibble)
```

# Introduction

I am studying on the third year of the Bachelor's degree in Data Engineering at Gdańsk University of Technology.

I am seeking a job to work part-time or remotely.

# Experience

```{r}
detailed_entries(tibble(what = 'ERGO Hestia',
                        when = 'April 2019 - Present',
                        with = 'Data Modeling Intern',
                        where = 'Sopot',
                        why = c('creating and maintaining Shiny applications',
                                'writing automation scripts in R and Python',
                                'improving code performance and quality',
                                'performing data mining activities')),
                 what, when, with, where, why)

detailed_entries(tibble(what = 'BEST SA',
                        when = 'July 2018 - November 2018',
                        with = 'Project-Based Internship - fuzzy address matching',
                        where = 'Gdynia',
                        why = c('analysing Polish address data',
                                'checking their correctness using string distance metrics',
                                'building a statistical tool that enhances their quality')),
                 what, when, with, where, why)
```

# Education

```{r}
detailed_entries(tibble(what = 'Gdańsk University of Technology',
                        with = 'Data Engineering',
                        when = 'October 2017 - February 2021',
                        where = 'Gdańsk',
                        why = c('Bachelor of Engineering (B. Eng.)',
                                'Faculty of Electronics, Telecommunications and Informatics',
                                'Faculty of Management and Economics')),
                 what, when, with, where, why)

detailed_entries(tibble(what = 'Stefan Żeromski High School No. 1 in Ełk',
                        with = 'Biochemical Profile',
                        when = 'September 2014 - May 2017',
                        where = 'Ełk'),
                 what, when, with, where)
```

# Skills

```{r}
detailed_entries(tibble(why = c('C1 Advanced CEFR Cambridge English Qualifications',
                                'fluency in R and creating Shiny applications',
                                'general knowledge of C/C++/Rcpp, Java, Scala, Python, and SQL',
                                'working knowledge of JavaScript, HTML, CSS, Bootstrap, and Git',
                                'vast knowledge of statistical and mathematical modeling methods',
                                'experience in using machine and deep learning algorithms',
                                'experience in modeling databases and data warehouses',
                                'experience in developing data pipelines and ETL/ELT processes')),
                 why = why)
```

# About me

I am a big fan of Manchester City Football Club and an Anglophile. In my free time I learn Spanish, watch YouTube videos about music and vocals, and read articles about data analysis. Also, in my free time I offer English tutor services. I make people aware that data.table is much faster than pandas.